Energy Regulation for Biologically-Inspired Robotics

### 2021-09-20 latex/nserc/contributions.tex
Almost-final editing pass of contributions

    \item \textbf{Software Developer, Neptec Technologies Corp., 2016 -- 2017}.
        My experience at Neptec was integral to my career because it convinced
        me to pursue research in robotics.
        Working at Neptec exposed me to many areas of electrical and computer
        engineering.
        I worked on several embedded software projects, my favourite of which
        was a control systems project.
        After completing this project, I decided to do a master's (and a PhD) so I
        could learn as much about control as possible.
        At Neptec I also learned to work on large software projects,
        and I became extremely proficient at software development, a skill which
        has served me well in all aspects of my research.

@@

\item \textbf{Science Payload Designer, Queen’s University Satellite Design
    Team (QSAT), 2017 -- 2018}. 
    I took on a mentorship role at QSAT, where I taught C++, Git, and information
    theory to the team’s software developers. I helped them organize
    the satellite codebase, managed all code reviews, and provided advice for my
    peers rather than writing software myself.

>>>>

    \item \textbf{Software Developer, Neptec Technologies Corp., 2016 -- 2017}.
        My experience at Neptec was integral to my career because it convinced
        me to pursue research in robotics.
        Working at Neptec exposed me to many areas of electrical and computer
        engineering.
        I worked on several embedded software projects, my favourite of which
        was a control systems project.
        After completing this work, I decided to do a master's (and a PhD) so I
        could learn as much about control as possible.
        At Neptec I also learned to work with large codebases,
        and I became extremely proficient at software development, a skill which
        has served me well in all aspects of my research.

@@

\item \textbf{Science Payload Designer, Queen’s University Satellite Design
    Team (QSAT), 2017 -- 2018}. 
    I took on a mentorship role at QSAT, where I taught C++, Git, and information
    theory to the team's software developers. I helped them organize
    the satellite codebase, managed all code reviews, and provided advice for my
    peers rather than writing software myself.
